---
output:
  html_document:
    keep_md: true
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

Tintle1
=======



This R Companion to 
[Introduction to Statistical Investigations (Preliminary Edition)](http:://www.hope.edu/isa/) 
by Nathan Tintle *et al*
provides

 * a companion text demonstrating how to use R to perform the analyses in that book
 * an R package (`Tintle1`) 

## Companion Text

 The campanion text is available 
 [as a PDF](https://github.com/rpruim/Tintle1/blob/master/Book/Tintle1.pdf) 
 
  * The authors are Randall Pruim and Lana Park.  
 
## R Package

The `Tintle1` package can be installed from github using

```{r eval=FALSE}
devtools::install_github("rpruim/Tintle1")
```

This package contains 

  * all of the data sets used in the book, and 
  * the `isa_snippet()` function which can be used to run any of 
`r length(Tintle1::isa_snippet())` code chunks from the campanion.  

For example:

```{r message=FALSE}
require(Tintle1)
require(mosaic)
```
```{r}
isa_snippet("Example1.3")
```

