---
output:
  html_document:
    keep_md: true
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
require(mosaic)
set.rseed(1234)
```

ISIwithR
=======

This R Companion to 
[Introduction to Statistical Investigations (Preliminary Edition)](http:://www.hope.edu/isi/) 
by Nathan Tintle *et al*
provides

 * a companion text demonstrating how to use R to perform the analyses in that book
 * an R package (`ISIwithR`) 

## Companion Text

 The campanion text is available as a PDF 
 [[to view]](Book/ISIwithR.pdf) or [[to download]](../../raw/master/Book/ISIwithR.pdf) 
 
  * The authors are Randall Pruim and Lana Park.  
 
## R Package

The `ISIwithR` package can be installed from github using

```{r, devtools, eval=FALSE}
devtools::install_github("rpruim/ISIwithR")
```

This package contains 

  * all of the data sets used in the book, and 
  * the `isa_snippet()` function which can be used to run any of 
`r length(ISIwithR::isi_snippet())` code chunks from the campanion.  

For example:

```{r, require, message=FALSE}
require(ISIwithR)
require(mosaic)
```
```{r, snippet}
isi_snippet("Exploration6.3.8")
```

